### 2016-03-16 section/0_intro.tex
finish revising explanation to figure 1

Figure~\ref{fig:GCC27733} shows a performance bug in GCC. 
Function \texttt{mult\_alg} is used to compute the best algorithm for 
multiplying \texttt{t}. It is so time consuming that developers used a
hash-table
\texttt{alg\_hash} to remember which \texttt{t} has been processed
in the past and what is the result. 
Unfortunately, a mistake in the type declaration of hash-table
entry \texttt{hash\_entry} makes the memoization useless for large \texttt{t},
severely hurting performance.
In reality, developers easily figured out that
\texttt{mult\_alg} is most correlated with the execution slowness, but
spent several weeks to finally figure out \texttt{mult\_alg}, 
containing 400 lines
of code, is
inefficient.
%If a tool can tell them not only which loop\footnote{Recursive functions are
%handled similarly as loops in this paper.}
%is the root cause but also why a loop is inefficient (i.e., lot of redundant
%computation and the need for better memoization in this example), 
%the diagnosis and bug fixing
%process would be much easier for developers.

>>>>

Figure~\ref{fig:GCC27733} shows a performance bug in GCC. 
Function \texttt{mult\_alg} is a recursive function 
that computes the best algorithm for 
multiplying \texttt{t}, a time-consuming computation. 
At run time, \texttt{mult\_alg} is often invoked for many times, and often
with the same parameter partly due to its recursive nature.
To avoid redundant computation across different instances of
\texttt{mult\_alg} with the same parameter, developers used a
hash-table
\texttt{alg\_hash} to remember which parameter \texttt{t} has been processed
in the past and what is the result. 
Unfortunately, a mistake in the type declaration of hash-table
entry \texttt{hash\_entry} makes the memoization useless for large \texttt{t}.
In many cases, a slow path is taken, when the fast path should have been taken.
This mistake does not affect software correctness, but it causes a large amount
of redundant computation\footnote{This problem will be considered as 
cross-loop redundancy later in this paper, as we consider
recursive functions as a special case of loops.} 
and hurts GCC performance severely,
causing hundreds of times slow down for GCC test cases.

Debugging this performance bug is challenging. According to 
the discussion forum of GCC, developers identified
\texttt{mult\_alg} as the most time-consuming function
through profilers early on. However, developers did not figure out 
whether \texttt{mult\_alg} is inefficient, which part of it is 
inefficient (\texttt{mult\_alg} is a large function with about 400 lines of 
code), and how it is inefficient, until several weeks later.

If a tool can tell developers not only \emph{which} loop or function is
responsible for execution slowness, but also \emph{why} and \emph{how}
the loop/function is inefficient, 
the diagnosis and bug fixing
process would be much easier.
